### 2016-12-30 Chapters/experiments.tex
Add strain validation figure

\subsection{S5 Text -- Strain construction}
\manuallabel{S5_Text}{S5~Text}

@@

\clearpage
\subsection{S6 Text -- Strain validation}
\manuallabel{S6_Text}{S6~Text}

@@

>>>>

\subsection{S5 Text -- DNA sequences used for the strain construction}
\manuallabel{S5_Text}{S5~Text}

@@

\clearpage
\subsection{S6 Text -- Strain validation in batch growing conditions}
\manuallabel{S6_Text}{S6~Text}

@@

Two type of strains were obtained

Before being used in the microscopy experiments, the strain characteristics were validated by

\begin{figure}[p]
\centering
\includegraphics[scale=1]{./Fig/suppinfo_caract}
\caption{
\textbf{Growth curves in M9~0.2\% glucose for the \textit{rpsB-gfp} and \textit{rpsB-mCherry} strains.}
Growth and measurements were performed in a 96-well microplate placed in a Tecan infinite 200 pro reader thermostated at 37$^\circ$C.
We monitored 4 wells inseminated with the WT strain, the \textit{rpsB-gfp} strain, and the \textit{rpsB-mCherry} strain, for a total of 12 wells each containing 150~$\mu$L of growth medium.
Curves were shifted in time to correct for pipetting variability in the insemination process (-50 min for WT, and -20 min for \textit{rpsB-mCherry}).
\textit{(A)}~The light absorbance as measured by the Tecan microplate reader, corrected for background by removing well containing clean M9.
The superposition of the curves indicates similar growth rates between the WT and the modified strains.
\textit{(B)}~The fluorescence measured in the wells, expressed in Relative Fluorescence Units (RFU).
Green fluorescence (485nm excitation, 535nm reception) is measured for the WT (dashed lines) and the \textit{rpsB-gfp} (solid lines) strains.
Red fluorescence (560nm excitation, 635nm reception) is measured for the WT (dashed lines) and the \textit{rpsB-mCherry} (solid lines) strains.
As can be seen, fluorescence levels of the modified strains (solid lines) are far above the autofluorescence measured on the WT strain.
\textit{(C)}~The ratio of fluorescence over absorbance, a proxy for the fluorescence concentration in the cells.
Autofluorescence background was corrected by removing the autofluorescence measured on the WT wells.
We observe a strange increase in fluorescence concentration for the \textit{rpsB-mCherry} strain at stationary phase, something that is not visible on the \textit{rpsB-gfp} strain.
Before each measurement cycle, the following procedure was applied: shaking (Orbital 6mm) for 30~s, shaking (Linear 6mm) for 30~s, waiting for 5~s.
}
\label{fig:suppinfo_caract}
\end{figure}
